Model of lens candidates from Space Warps CFHTLS

### 2016-05-20 paper2.tex
update table (autogenerated)

\lenstitle{SW01 (ASW0004dv8)}
  This is some text that says something more than this line.

\lenstitle{SW08 (ASW00099ed)}
  Simple lens with two images;
  model has minor arthefacts.

\lenstitle{SW11 (ASW0002qtn)}
  Simple small arc;
  model nedes minor refinement;
  quite low mass ratio

\lenstitle{SW12 (ASW0003wsu)} 
  faint arc, bright overall situation, no counter image;
  has good model;
  low Mstel and low Mlens

\lenstitle{SW21 (ASW0004m3x)} 
  clear arc, no counter image; inbetween two external sources;
  model needs work, predicts additional images. play with external mass / sheer?
  Mass ratio low.

\lenstitle{SW27 (ASW0006jh5)} 
  (really plausible?)
  unclear situation, but arc is visible;
  model shows extended arc not there in org image;
  mass ratio ok

\lenstitle{SW31 (ASW00021r0)} 
  (really plausible?)
  noisy situation, unclear images, potential external mass interfering;
  model ok'ish, hard to say;
  high mass ratio

\lenstitle{SW33 (ASW0003s0m)}
  clear picture, two image situation;
  model simple, but ok. arc too much extended;
  masses in the middle, but rather high ratio

\lenstitle{SW36 (ASW000096t)} 
  noisy picture, many possible external masses, faint images;
  model predicts additional images, needs more work, arc too extended;
  masses look ok

\lenstitle{SW38 (ASW0009cp0)} 
  quite clean picture, two bright minima, counter image hidden;
  model fine
  really hi stellar mass

\lenstitle{SW43 (ASW0001c3j)} 
  clean situation, faint arc'ish images;
  model needs work, shows additional images, strange arc (LHD);
  very high Mstel

\lenstitle{SW45 (ASW00024id)}
  ring like structure, very clean
  usual problems with rings, otherwise model quite ok actually;
  very high Mstel

\lenstitle{SW46 (ASW00024q6)} 
  yellow'ish arc, two image configuration;
  model ok;
  masses ok

\lenstitle{SW52 (ASW0006a07)} 
  (no imgs)

\lenstitle{SW54 (ASW0007sez)} 
  white lens, fuzzy ring like structure;
  model really good, given ring like;
  masses ok

\lenstitle{SW58 (ASW0007iwp)} 
  nice arc, no counter image;
  model prediction really good;
  masses ok
  good example of plausible

\subsubsection{grouplens}

\lenstitle{SW36 (ASW000096t)}
(like 4dv8 collective modelling)

@@

\lenstitle{SW04 (ASW0009cjs)} 
  noisy field, possible group lens, but images not typical? (no arclike structure);
  model fail (input errors);
  Mlens too high (10e13)

\lenstitle{SW06 (ASW0008swn)}
  green images, elongated lens, images on strange positions?;
  model ok'ish, but mass distr. doesn't reflect visuals;
  masses ok

\lenstitle{SW07 (ASW0007e08)} 
  (no img)

\lenstitle{SW13 (ASW00047ae)} 
  croweded situation unclear setup;
  model failed, predicts additional images;
  masses ok

\lenstitle{SW15 (ASW0004nan)} 
  no counter image (should be visible)?
  model ok'ish;
  Mlens on the lower end

\lenstitle{SW17 (ASW0005rnb)} 
  two image setup, but arcish structure of images missing;
  model failed, predicts additional images, rednering failed;

\lenstitle{SW19 (ASW0001ld7)} 
  asymmetry / really extended arc and no counter image rather no lensing configuration;
  rendering ok'ish, model predicts additionla images;
  Mstel and Mlens way too low (e10 / e11)

\lenstitle{SW24 (ASW00050sk)} 
  unclear / noisy situation, shape of arc strange;
  model ok;
  mass ration close to unity

\lenstitle{SW32 (ASW0004iye)} 
  (no img)

\lenstitle{SW35 (ASW0004wgd)} 
  hard to say, doesn't look convincing, but neither totally off
  modell ok;
  masses as well;

\lenstitle{SW44 (ASW0002k40)} 
  (no img);
  very old model;
  hi mass ratio

\lenstitle{SW47 (ASW0003r6c)} 
  two images, no arcish structre.. too far away from lens?;
  model predicts additional images;
  quite high mass ratio

\lenstitle{SW51 (ASW0006e0o)} 
  (no img)

\lenstitle{SW56 (ASW0007pga)} 
  very ellyptical lens, images not really arcish;
  model failed, predicts additional images;
  masses ok

\lenstitle{SW57 (ASW0008pag)} 
  point mass / group lens interfering? symertry of arc off;
  model failed completly;
  Mlens too high

@@

\lenstitle{SW10 (ASW0002bmc)} 
  very elliptical setup, unlikley to be a lens;
  model failed totally

\lenstitle{SW16 (ASW0009bp2)} 
  very faint images

\lenstitle{SW18 (ASW0007hu2)} 
  model failed completly

\lenstitle{SW20 (ASW0002dx7)} 
  faint white images, rather substuctre of ``lens'' ??

\lenstitle{SW22 (ASW0009ab8)} 
  very faint images, group configuration;
  model predicts additional images;
  mass ration close to unity

\lenstitle{SW23 (ASW0003r61)} 
  (no img)

\lenstitle{SW26 (ASW0005ma2)} 
  similar to SW10

\lenstitle{SW34 (ASW00051ld)} 
  (no img)

\lenstitle{SW41 (ASW0008xbu)} 
  similar to SW10. very ellyptical lens

\lenstitle{SW42 (ASW00096rm)} 
  ring like structure, but very strange distribution;
  model not too bad, brightnesses off;
  stellar mass way too lower

\lenstitle{SW53 (ASW00070vl)} 
  images don't look liked lensed;
  model predicts additional images

@@

\lenstitle{SW03 (ASW0006mea)}

\lenstitle{SW14 (ASW0004xjk)}

\lenstitle{SW25 (ASW00007mq)}

\lenstitle{SW30 (ASW0002p8y)}

\lenstitle{SW37 (ASW00086xq)}

\lenstitle{SW39 (ASW0005qiz)}

\lenstitle{SW40 (ASW0008wmr)}

\lenstitle{SW48 (ASW0000g95)}

\lenstitle{SW49 (ASW00007ls)}

\lenstitle{SW50 (ASW00008a0)}

\lenstitle{SW55 (ASW0007t5y)}

\lenstitle{SW59 (ASW00085cp)}

>>>>

@@

@@

@@

\lenstitle{SW03 (ASW0006mea)}
\lenstitle{SW14 (ASW0004xjk)}
\lenstitle{SW25 (ASW00007mq)}
\lenstitle{SW30 (ASW0002p8y)}
\lenstitle{SW37 (ASW00086xq)}
\lenstitle{SW39 (ASW0005qiz)}
\lenstitle{SW40 (ASW0008wmr)}
\lenstitle{SW48 (ASW0000g95)}
\lenstitle{SW49 (ASW00007ls)}
\lenstitle{SW50 (ASW00008a0)}
\lenstitle{SW55 (ASW0007t5y)}
\lenstitle{SW59 (ASW00085cp)}
